\tool: Revisiting BadUSB with Type-C

### 2021-01-30 WOOT/Files/badusb.tex
manually fix a conflict.

\textbf{Scripting Mode.} This mode majorly relies on the ``HID Emulator'' to
send constructed HID packet to the victim. These constructed HID packets are
interpreted by the victim as valid keystrokes and mouse moves. Thus, the
attacker can executes arbitrary scripts on the victim's device. This is the
function of the original BadUSB. Based on this, we made the following
improvement.

First, \tool supports defense-bypassing. As the original BadUSB cannot get
feedback from the victim, defense mechanisms like GoodUSB
\cite{tian2015defending} are sufficient to prevent these BadUSB attacks.
However, these defense mechanisms leverage visual notification to block access
for unknown USB devices. This means that when the defense request authorization
from the user, our \tool is able to capture the content of authorization
challenge and bypass it. After the defense is bypassed, \tool continues the
emulation and script execution, resulting in a successful attack.

Moreover, as the mouse relies on the visual feedback to work properly, its
emulation and automation were not supported by the original version of BadUSB.
Yet with the video output support from USB 3.x, our \tool implements
full-functional mouse emulation. This function enables attacks toward pure GUI
programs and shows great potential in the mobile attack scenario. Details can
be obtained in Section~\ref{sec:experiment}.

The advantage of this mode is that it archives defense bypass and attack
feedback with video streaming.  \fengwei{I don't understand the sentence below.}\hongyi{Fixed, I think it's redundant and less important}
%As mentioned above, we only require video stream at the beginning (defense
%bypass) and the end (result feedback) of the attack.
Moreover, with mouse
supported, \tool extends the original BadUSB attack surface and perform well in
mobile device.

\textbf{Privacy Extraction Mode.} \tool under this mode does not emulate other
USB device and solely relies on the video stream function of USB 3.x; it uses
``Video Capture'' component to transmit the stream to embedded ``Single Board Computer''\fengwei{What is embedded computer? Do we define this in the previous\hongyi{Fixed by using the term mentioned in Figure}
text?}. The victim's device would mistakenly treat \tool as an external monitor
and output its video stream. This stream is latter processed by the embedded
computer to extract private data.

When running in this mode, \tool passively processes the victim's video stream
and detect for ``valuable'' private data.  The data is considered as
``valuable'' or not is decided by a customized detector, we implement a simple
payment code detector for the demonstration purpose. Though this detector is
simple to implement, we successfully transfer money from the victim to the
attacker. More detail can be obtained in Section~\ref{sec:experiment}.

It is worth mentioning that \tool under this mode is completely passive, making
it hard to be detected and defended. With different detector implemented, \tool
under this mode is capable of serving more purposes.

\textbf{Remote Control Mode.} In \tool, we have implemented all components
required to control a computer/mobile device remotely, including a video stream
and a keyboard/mouse emulation. Thus with all components enabled, not only will
the victim's device treat \tool as an external display, but also a valid HID
input source. Hence we can archive complete hijack of victim's device.

\tool under this mode follows a simple logic. \tool will receive video stream
from the victim's device and redirect it to the attacker via GSM/WiFi. In the
meanwhile, \tool also receives keystrokes and mouse movement from the attacker
through GSM/WiFi and replay them to the victim by the USB emulation.

This mode enable attacker to perform delicate operation that is beyond
automation. Moreover, this mode provides a backdoor that does not require host
network and thus is undetectable by the firewall running on the host machine.
%\hongyi{I think this is a quite good selling point?}\shuqing{Agree with
%Hongyi.}

The advantage of this mode is that it can completely hijack the victim device
and provide a backdoor beyond detection of firewalls. But this complete control
also comes with the price of high power consumption and risk of being detected
by the user.

>>>>

\textbf{Scripting Mode.} This mode majorly relies on the ``HID Emulator'' in the Figure~\ref{fig:attack_model} to
send constructed HID packet to the victim. These constructed HID packets are
interpreted by the victim as valid keystrokes and mouse moves. Thus, the
attacker can executes arbitrary scripts on the victim's device. This is the
function of the original BadUSB. Based on this, we made the following
improvements.

First, \tool supports defense-bypassing. As the original BadUSB cannot get
feedback from the victim, defense mechanisms like GoodUSB~\cite{tian2015defending} are sufficient to prevent these BadUSB attacks.
However, these defense mechanisms leverage visual notification to block access
for unknown USB devices. This means that when the defense requests authorization
from the user, our \tool is able to capture the content of authorization
challenge and bypass it. After the defense is bypassed, \tool continues the
emulation and script execution, resulting in a successful attack.

Moreover, as the mouse relies on the visual feedback to work properly, its
emulation and automation were not supported by the original version of BadUSB.
Yet with the video output support from USB 3.x, our \tool implements a
full-functional mouse emulation. This function enables attacks toward pure GUI
programs and shows attacks in the mobile attack scenarios. Details can
be obtained in Section~\ref{sec:experiment}.

The advantage of this mode is that it archives defense bypass and attack
feedback with video streaming.  
%\fengwei{I don't understand the sentence below.}\hongyi{Fixed, I think it's redundant and less important}
%As mentioned above, we only require video stream at the beginning (defense
%bypass) and the end (result feedback) of the attack.
Moreover, with mouse
supported, \tool extends the original BadUSB attack and results in further attacks in
mobile devices.

\textbf{Privacy Extraction Mode.} \tool under this mode does not emulate other
USB device and solely relies on the video stream function of USB 3.x; it uses
``Video Capture'' component as shown in the Figure~\ref{fig:attack_model} to transmit the stream to the embedded ``Single Board Computer''.
%\fengwei{What is embedded computer? Do we define this in the previous\hongyi{Fixed by using the term mentioned in Figure}
%text?}. 
The victim's device would mistakenly treat \tool as an external monitor
and output its video stream. This stream is latter processed by the embedded
computer to extract sensitive data.

When running in this mode, \tool passively processes the victim's video stream
and detect for ``valuable'' private data.  The data is considered as
``valuable'' or not is decided by a customized detector, we implemented a simple
payment code detector for the poof-of-concept purpose, which demonstrates that we successfully transfer money from a victim to an
attacker. More detail can be obtained in Section~\ref{sec:experiment}.

It is worth mentioning that \tool under this mode is completely passive, making
it hard to be detected. With different detector implemented, \tool
under this mode is capable of serving more purposes.

\textbf{Remote Control Mode.} In \tool, we have implemented all components
required to control a computer/mobile device remotely, including a video stream
and a keyboard/mouse emulation. Thus with all components enabled, not only
the victim's device treat \tool as an external display, but also a valid HID
input source. Hence we can archive complete hijack of victim's device.

\tool under this mode follows a simple logic. \tool receives video stream
from the victim's device and redirect it to the attacker via GSM/WiFi. In the
meanwhile, \tool also receives keystrokes and mouse movement from the attacker
through GSM/WiFi and replays them to the victim by the USB emulation.

This mode enable attacker to perform delicate operations that are beyond
automation. Moreover, this mode provides a backdoor that does not require host
network and thus is undetectable by the firewall running on the host machine.
%\hongyi{I think this is a quite good selling point?}\shuqing{Agree with
%Hongyi.}

The advantage of this mode is that it can completely hijack the victim device
and provide a backdoor beyond detection of firewalls; however, this complete control
also comes with the price of high power consumption and risk of being detected
by the user.
